Dark Control:\\ Towards a Unified Account of Default Mode Function\\ by Markov Decision Processes

### 2017-12-08 paper/paper.tex
finalizing rebuttal

\subsection{Markov decision processes}
Reinforcement learning (RL) has had considerable success in modeling many real-world problems, including super-human performance in complex video games \citep{mnih2015},
robotics \citep{ng2004,abbeel2004},
and strategic board games like the breakthrough results upon recently on the game of Go \citep{silver2016mastering} considered to be a milestone benchmark in artificial intelligence.
We emphasize that the brain in general, and the DMN in particular,
is a physical system governed by the laws of
physics and can be formally described
by Markov processes at a sufficiently coarse scale.
It has indeed been previously proposed \citep{tegmark2016improved} that
any system obeying the laws of classical physics can be accurately modeled as a Markov process as long as the time
step is sufficiently short.

In artificial intelligence and machine learning, a popular computational model for
multi-step decision processes in such an environment are
MDPs \citep{sutton1998reinforcement}.
% For the remainder of this paper, for the sake of simplicity
% we use the abbreviation ``MDP'' to refer to the special case
% of \textit{Partially Observable Markov Decision Processes}.
An MDP operationalizes a sequential decision process
in which it is assumed that environment dynamics are determined by a Markov process,
but the agent cannot directly observe the underlying state.
Instead, the agent tries to optimize a \textit{subjective} reward
signal (i.e., likely to be different for another agent in the same state),
by maintaining probability distributions over actions according to their expected utility.
% This is performed alongside each transition in the state space of the environment
%  and maintains a probability distribution over the set of possible
% states.
% % , based on a set of observations and observation probabilities.
This is a minimal set of assumptions that can be made about an environment faced by an agent engaged in interactive learning.

>>>>

\subsection{Markov decision processes}
Reinforcement learning (RL) has had considerable success in modeling many real-world problems, including super-human performance in complex video games \citep{mnih2015},
robotics \citep{ng2004,abbeel2004},
and strategic board games like the breakthrough results upon recently on the game of Go \citep{silver2016mastering} considered to be a milestone benchmark in artificial intelligence.
% We emphasize that the brain in general, and the DMN in particular,
% is a physical system governed by the laws of
% physics and can be formally described
% by Markov processes at a sufficiently coarse scale.
% It has indeed been previously proposed \citep{tegmark2016improved} that
% any system obeying the laws of classical physics can be accurately modeled as a Markov process as long as the time
% step is sufficiently short.
In artificial intelligence and machine learning, a popular computational model for
multi-step decision processes in such an environment are
MDPs \citep{sutton1998reinforcement}.
% For the remainder of this paper, for the sake of simplicity
% we use the abbreviation ``MDP'' to refer to the special case
% of \textit{Partially Observable Markov Decision Processes}.
An MDP operationalizes a sequential decision process
in which it is assumed that environment dynamics are determined by a Markov process,
but the agent cannot directly observe the underlying state.
Instead, the agent tries to optimize a \textit{subjective} reward
signal (i.e., likely to be different for another agent in the same state),
by maintaining probability distributions over actions according to their expected utility.
% This is performed alongside each transition in the state space of the environment
%  and maintains a probability distribution over the set of possible
% states.
% % , based on a set of observations and observation probabilities.
This is a minimal set of assumptions that can be made about an environment faced by an agent engaged in interactive learning.
